---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

Rocking R at UMCCR
==================

[![Travis build status](https://travis-ci.org/umccr/rock.svg?branch=master)](https://travis-ci.org/umccr/rock)
[![Coverage status](https://codecov.io/gh/umccr/rock/branch/master/graph/badge.svg)](https://codecov.io/github/umccr/rock?branch=master)

`rock` is an R package that (hopefully) helps with the day to day bioinformatics
life at UMCCR (UniMelb Centre for Cancer Research).

## Installation

You can install the development version of `rock` from [GitHub](https://github.com/umccr/rock) with:

```r
# install.packages("devtools") # if not pre-installed
devtools::install_github("umccr/rock") # master version
devtools::install_github("umccr/rock@v1.2.3") # release v1.2.3
devtools::install_github("umccr/rock@abcd") # commit abcd
```

## Circos Plots

* We can generate circos plots using the
  [OmicCircos](https://bioconductor.org/packages/release/bioc/html/OmicCircos.html)
  Bioconductor R package.

```{r}
library(rock)
```


* Start by preparing the SV and CNV calls:

```{r circos-prep, message=FALSE}
manta <- system.file("extdata", "HCC2218_manta.vcf", package = "pebbles")
cnvkit <- system.file("extdata", "HCC2218_cnvkit-call.cns", package = "pebbles")
facets <- system.file("extdata", "HCC2218_facets_cncf.tsv", package = "pebbles")
sv_manta <- prep_manta_vcf(manta)
cn_facets <- prep_facets_seg(facets)
cn_cnvkit <- prep_cnvkit_seg(cnvkit)
```

* Now we can generate a circos plot with Manta links and FACETS/CNVkit segments:

```{r circos-plot-manta-cnvkit, fig.width=8, fig.height=8, warning=FALSE}
plot_circos(sv = sv_manta, cnv = cn_cnvkit)
```

```{r circos-plot-manta-facets, fig.width=8, fig.height=8, warning=FALSE}
plot_circos(sv = sv_manta, cnv = cn_facets)
```
