---
title: "Introduction to rock"
author: "Peter Diakumis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE, message=FALSE}
require(rock)
```

## Hello

Say hello to each element:

```{r}
x <- c("Foo", "Bar", "Baz")
hello(x)
```

## Circos Plots

* Start by preparing the SV and CNV calls. Note that `prep_manta_vcf` requires
  [bcftools](https://samtools.github.io/bcftools/bcftools.html) to be in
  your PATH. If you are using RStudio, your PATH can be read if you open
  RStudio (or an RMarkdown/R script) from the terminal.

```{r circos-prep, message=FALSE}
manta <- system.file("extdata", "HCC2218_manta.vcf", package = "pebbles")
cnvkit <- system.file("extdata", "HCC2218_cnvkit-call.cns", package = "pebbles")
facets <- system.file("extdata", "HCC2218_facets_cncf.tsv", package = "pebbles")
sv_manta <- prep_manta_vcf(manta)
cn_facets <- prep_facets_seg(facets)
cn_cnvkit <- prep_cnvkit_seg(cnvkit)
```

* Now we can generate a circos plot with Manta links and FACETS/CNVkit segments
  (note that the `Warning` message below is due to a hack used in the OmicCircos
  code, where a matrix with numbers and characters is coerced to numeric.
  Just don't worry about it..):

```{r circos-plot-manta-cnvkit, fig.width=8, fig.height=8}
plot_circos(sv = sv_manta, cnv = cn_cnvkit)
```

```{r circos-plot-manta-facets, fig.width=8, fig.height=8}
plot_circos(sv = sv_manta, cnv = cn_facets)
```
