---
title: "Introduction to rock"
author: "Peter Diakumis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE, message=FALSE}
require(rock)
```

## Hello

Say hello to each element:

```{r}
x <- c("Foo", "Bar", "Baz")
hello(x)
```

## Circos Plots

* Start by preparing the SV and CNV calls.

```{r circos-prep, message=FALSE}
manta <- system.file("extdata", "HCC2218_manta.vcf", package = "pebbles")
cnvkit <- system.file("extdata", "HCC2218_cnvkit-call.cns", package = "pebbles")
facets <- system.file("extdata", "HCC2218_facets_cncf.tsv", package = "pebbles")
titan <- system.file("extdata", "HCC2218_titan.segs.tsv", package = "pebbles")
purple <- system.file("extdata", "HCC2218_purple.cnv.tsv", package = "pebbles")

sv_manta <- prep_manta_vcf(manta)
cn_facets <- prep_facets_seg(facets)
cn_cnvkit <- prep_cnvkit_seg(cnvkit)
cn_titan <- prep_titan_seg(titan)
cn_purple <- prep_purple_seg(purple)
```

* Now we can generate a circos plot with Manta links and FACETS/CNVkit/TitanCNA segments
  (note that the `Warning` message below is due to a hack used in the OmicCircos
  code, where a matrix with numbers and characters is coerced to numeric.
  Just don't worry about it..):

### Manta with CNVkit

```{r circos-plot-manta-cnvkit, fig.width=8, fig.height=8}
plot_circos(sv = sv_manta, cnv = cn_cnvkit)
```

### Manta with FACETS

```{r circos-plot-manta-facets, fig.width=8, fig.height=8}
plot_circos(sv = sv_manta, cnv = cn_facets)
```

### Manta with TitanCNA

```{r circos-plot-manta-titan, fig.width=8, fig.height=8}
plot_circos(sv = sv_manta, cnv = cn_titan)
```

### Manta with PURPLE

```{r circos-plot-manta-purple, fig.width=8, fig.height=8}
plot_circos(sv = sv_manta, cnv = cn_purple)
```

## Piano Plots

* We can generate 'piano' plots to compare CNV calls from multiple
  callers or samples.
  
```{r piano-plot-cnvkit-facets-purple-titan1, fig.width=8, fig.height=7}
plot_piano(list(cnvkit = cn_cnvkit, facets = cn_facets, purple = cn_purple, titan = cn_titan))
```
  
  
